Global Climate and Atmospheric Composition of the Ultra-Hot Jupiter WASP-103\lowercase{b} from \HST\ and \Spitzer\ Phase Curve Observations

### 2018-05-08 ApJ_submit_v4/ms.tex
correct zhang reference

\acknowledgments
Support for \textit{HST} program GO-15050 was provided by NASA through a grant
from the Space Telescope Science Institute, which is operated by the Association
of Universities for Research in Astronomy, Inc., under NASA contract NAS
5-26555. Support for \textit{Spitzer} program 11099 was provided by NASA through
an award issued by JPL/Caltech.  The data presented in this paper were obtained
from the Mikulski Archive for Space Telescopes (MAST) and the NASA/IPAC Infrared
Science Archive. The Infrared Science Archive is operated by the Jet Propulsion
Laboratory, California Institute of Technology, under contract with the National
Aeronautics and Space Administration.  This work also made use of the Python
packages  SciPy and NumPy \citep{jones_scipy_2001, van2011numpy}. The authors
are grateful for helpful conversations with Caroline Morley, Thomas Beatty, Ming
Zhao, Kim Star Cartier, Hannah Diamond-Lowe, and Nick Cowan. We also thank the
organizers of the 2016 Santa Cruz Kavli Summer Program and the 2017 Ringberg
Atmospheres of Disks and Planets meeting for facilitating productive discussion
and collaboration.  J.L.B. acknowledges support from the David and Lucile
Packard Foundation.  J.M.D. acknowledges support from the European Research
Council (ERC) under the programme Exo-Atmos (grant agreement no. 679633). G.W.H.
and M.H.W. also acknowledge long-term support from Tennessee State University
and the State of Tennessee through its Centers of Excellence Program. M.R.L.
acknowledges NASA XRP grant NNX17AB56G for partial support of the theoretical
interpretation of the data, as well as the ASU Research Computing staff for
support with the Saguaro and Agave compute clusters. Finally, we thank the
anonymous referee for a thoughtful and detailed report that improved the quality of the
paper.

>>>>

\acknowledgments
Support for \textit{HST} program GO-15050 was provided by NASA through a grant
from the Space Telescope Science Institute, which is operated by the Association
of Universities for Research in Astronomy, Inc., under NASA contract NAS
5-26555. Support for \textit{Spitzer} program 11099 was provided by NASA through
an award issued by JPL/Caltech.  The data presented in this paper were obtained
from the Mikulski Archive for Space Telescopes (MAST) and the NASA/IPAC Infrared
Science Archive. The Infrared Science Archive is operated by the Jet Propulsion
Laboratory, California Institute of Technology, under contract with the National
Aeronautics and Space Administration.  This work also made use of the Python
packages  SciPy and NumPy \citep{jones_scipy_2001, van2011numpy}. The authors
are grateful for helpful conversations with Caroline Morley, Thomas Beatty, Ming
Zhao, Kimberly Cartier, Hannah Diamond-Lowe, and Nick Cowan. We also thank the
organizers of the 2016 Santa Cruz Kavli Summer Program and the 2017 Ringberg
Atmospheres of Disks and Planets meeting for facilitating productive discussion
and collaboration.  J.L.B. acknowledges support from the David and Lucile
Packard Foundation.  J.M.D. acknowledges support from the European Research
Council (ERC) under the programme Exo-Atmos (grant agreement no. 679633). G.W.H.
and M.H.W. also acknowledge long-term support from Tennessee State University
and the State of Tennessee through its Centers of Excellence Program. M.R.L.
acknowledges NASA XRP grant NNX17AB56G for partial support of the theoretical
interpretation of the data, as well as the ASU Research Computing staff for
support with the Saguaro and Agave compute clusters. Finally, we thank the
anonymous referee for a thoughtful and detailed report that improved the quality of the
paper.
